---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggtextcounts

<!-- badges: start -->
<!-- badges: end -->

The goal of ggtextcounts is to make it easy to count word frequencies in natural
language in a data frame column.

## Installation

You can install the development version of ggtextcounts from with:

``` r
# install.packages("devtools")
devtools::install_github("alicirce/ggtextcounts")
```

## Example: Counting mentions in a data frame

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggtextcounts)
library(dplyr, warn.conflicts = FALSE)
example_data <- data.frame(
  chapter = c(1:3),
  text = c(
    "Once upon a time there was a cat. The cat's name was Jennifer.",
    "This cat was unlike other cats, in that she had wings.",
    "Each wing was feathered. She loved to spread her wings and fly."
  )
)
```
With word boundaries, "cats" isn't counted in the second row:
```{r}
count_mentions_in_dataframe(
  example_data,
  words = c("cat", "wing"),
  ignore_case = TRUE,
  word_boundaries = TRUE
)
```

Without word boundaries, "cat" is counted twice in the second row
```{r}
cat_wing_counts <- count_mentions_in_dataframe(
  example_data,
  words = c("cat", "wing"),
  ignore_case = TRUE,
  word_boundaries = FALSE
)
cat_wing_counts
```

## Plotting counts

Lollipop plots are a visually attractive way of plotting counts.

```{r fig.height = 1.5, fig.width = 2}
library(ggplot2)
cat_wing_counts %>%
  group_by(word) %>%
  summarize(n = sum(mentions)) %>%
  ggplot() +
  aes(y = word, x = n) +
  geom_h_lollipop()
```
